Measuring individual differences in the understanding of gaze cues across the lifespan

### 2022-04-08 paper/manuscript.Rmd
review ext vali section

## Study versions
We designed two study versions which can be chosen according to the researchers' need: there is a continuous *hedge* version and a discrete *box* version. Both versions use the same first training trial and then differ in the consecutive training and test trials. 
In the *hedge* version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version). 
Here, the dependent variable is imprecision, which is defined as the absolute difference between the target's true x coordinate and the x coordinate of the participant’s click.
In the *box* version, participants are asked to click on a box that hides the target. Researchers have the choice of how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations. Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses. 
Note that in the test trials of both study versions, the target flight is covered by a hedge. In the *hedge* version, the hedge then shrinks to a minimum height required to cover the target's end location. In the *box* version, the hedge shrinks completely. The boxes then hide the target's final destination.

(ref:figlab1) **Study setup**. 
(a) Infrastructure for online testing. (i) Subjects aged 3 – 99+ can participate. Data collection can take place anywhere: at home, in kindergartens or research institutes. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure local servers.
(b) Continuous *hedge* version of the balloon finding task. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. 
(c) Discrete *box* version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set individually.

@@

## Randomization
All agents and target colors appear equally often and are not repeated in more than two consecutive trials. The randomization of the target end location depends on the study version. In the *hedge* version, the full width of the screen is divided into ten bins. Exact coordinates within each bin are then randomly generated. In the *box* version, the target randomly lands in one of the boxes. As with agent and color choice, each bin/box occurs equally often and can only occur twice in a row.

@@

## Results
(ref:figlab2) **Measuring interindividual variation**. 
(a) Developmental trajectory in continuous *hedge* version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(b) Internal consistency (odd-even split) in hedge child sample. (c) Internal consistency in hedge adult sample. (d) Test-retest reliability in hedge child sample. (e) Test-retest reliability in hedge adult sample.
(f) Developmental trajectory in discrete *box* version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(g) Internal consistency (odd-even split) in box child sample. (h) Internal consistency in box adult sample. (i) Test-retest reliability in box child sample. (j) Test-retest reliability in box adult sample.
Regression lines with 95% CI show product-moment-correlations with *Pearson*'s correlation coefficient *r.* 
Large data points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small data points show the mean performance for each subject. Shape of data points represents data collection mode: opaque round circles stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection. Color of data points represent each age group (binned by year).

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics(c("../figures/gafo_results.png"))
``` 
```{r agemodels}
mAgeHedge <- readRDS(file = "../saves/mAgeHedge.rds") 
mAgeBox <- readRDS(file = "../saves/mAgeBox.rds") 
```

@@

## Analysis
We assessed reliability in two ways. 
First, we focused on the internal consistency by calculating splithalf reliability coefficients. For each subject, trials were split into odd and even and performance scores per part were correlated against each other using *Pearson* correlation coefficients. We took the data of the first test day and defined performance according to study version: in the hedge version, performance referred to the absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the proportion of correct choices. 
As a recent paper by @pronk2021methods suggested, there are various less well-known split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design. To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position. First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling. Analyses were run using the function `by_split`from the `splithalfr` package [@pronk2021methods].
Second, we assessed the test-retest reliability. We calculated performance scores (depending on study version as described above) for each individual in each test session and correlated those using *Pearson* correlation coefficients. Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach. We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`). For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
The model computes a correlation between the participant specific estimates for each test day. This can be interpreted as the test-retest reliability. By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information. Most importantly, the model allows us to get an age-independent estimate for reliability. This rules out the possibility that a high correlation between test days arises from domain general cognitive maturation processes instead of study-specific inter-individual differences.

@@

# Exploring the external validity of our task
Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings. 
```{r extvali_sample}
extvali <- testtrials %>% 
  filter(ageInYears < 6) %>%
  mutate(
        symmetricPosition = case_when(
                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1, 
                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3, 
                                  targetPosition == "2" | targetPosition == "9" ~ 4,
                                  targetPosition == "1" | targetPosition == "10" ~ 5, 
                       ), 
  ) %>% 
  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, symmetricPosition) %>% 
  group_by(subjID) %>% 
  # so that all models run with same nr of subjects
  drop_na()

@@

## Analysis
To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version). The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants. Therefore, our null model closely resembled the structure from our first analysis (section *Does the balloon finding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`). 
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome. For the target position, we summarized the two adjacent bins into one imaginary box. For the click responses, we created imaginary box boundaries around the target's landing position and assessed whether the participant's response fell into this imaginary box. Across the two study versions, we could consequently model the participant's correct response (0/1) using a Bernoulli distribution with a logit link function.
For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subjects entered childcare. 
In addition, we calculated three index scores. First, we calculated a sibling variety score according to @peterson2000kindred. Second, we implemented the modified version of @cassidy2005theory (for more details, see Supplements). Third, based on our own data exploration we calculated the amount of peer exposure as the number of siblings and the average hours spent in childcare (all z-transformed). 
We compared the models using WAIC (widely applicable information criterion) scores and weights. As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit. WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

## Results
[TODO] All effects except when a child entered childcare positively influence performance. 
The effect sizes are all small and 95% CIs mostly include zero. It is remarkable, however, that we were able to detect a relationship between a fundamental social-cognitive ability and very distant, real life demographics.

(ref:figlab4) **External validity of the balloon finding task**. 
[TODO] WAIC scores and weights can be found in the Supplements section. 
```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
knitr::include_graphics("../figures/extvali-posteriorsample.png")
```

# Discussion
## Limitations
## Future development / extending the task

@@

#### WAIC scores and weights of the model comparison
As can be seen, ELPD difference scores are smaller than their respective standard errors. WAIC scores between models don't differ substantially. All effects except when a child entered childcare positively influence performance. 
```{r extvali_results}
extvali_models <- readRDS(file = "../saves/extvali-results.rds")
knitr::kable(extvali_models)
```

>>>>

## Study versions
We designed two study versions which can be chosen according to the researchers' need: there is a continuous hedge version and a discrete box version. Both versions use the same first training trial and then differ in the consecutive training and test trials. 
In the hedge version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version). 
Here, the dependent variable is imprecision, which is defined as the absolute difference between the target's true x coordinate and the x coordinate of the participant’s click.
In the box version, participants are asked to click on a box that hides the target. Researchers have the choice of how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations. Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses. 
Note that in the test trials of both study versions, the target flight is covered by a hedge. In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location. In the box version, the hedge shrinks completely. The boxes then hide the target's final destination.

(ref:figlab1) **Study setup**. 
(a) Infrastructure for online testing. (i) Subjects aged 3 – 99+ can participate. Data collection can take place anywhere: at home, in kindergartens or research institutes. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure local servers.
(b) Continuous hedge version of the balloon finding task. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. 
(c) Discrete box version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set individually.

@@

## Randomization
All agents and target colors appear equally often and are not repeated in more than two consecutive trials. The randomization of the target end location depends on the study version. In the hedge version, the full width of the screen is divided into ten bins. Exact coordinates within each bin are then randomly generated. In the box version, the target randomly lands in one of the boxes. As with agent and color choice, each bin/box occurs equally often and can only occur twice in a row.

@@

## Results
(ref:figlab2) **Measuring interindividual variation**. 
(a) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(b) Internal consistency (odd-even split) in hedge child sample. (c) Internal consistency in hedge adult sample. (d) Test-retest reliability in hedge child sample. (e) Test-retest reliability in hedge adult sample.
(f) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(g) Internal consistency (odd-even split) in box child sample. (h) Internal consistency in box adult sample. (i) Test-retest reliability in box child sample. (j) Test-retest reliability in box adult sample.
Regression lines with 95% CI show product-moment-correlations with *Pearson*'s correlation coefficient *r.* 
Large data points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small data points show the mean performance for each subject. Shape of data points represents data collection mode: opaque round circles stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection. Color of data points represent each age group (binned by year).

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics(c("../figures/gafo_results.png"))
```

```{r agemodels}
mAgeHedge <- readRDS(file = "../saves/mAgeHedge.rds") 
mAgeBox <- readRDS(file = "../saves/mAgeBox.rds") 
```

@@

## Analysis
We assessed reliability in two ways. 
First, we focused on the internal consistency by calculating splithalf reliability coefficients. For each subject, trials were split into odd and even and performance scores per part were correlated against each other using *Pearson* correlation coefficients. We took the data of the first test day and defined performance according to study version: in the hedge version, performance referred to the absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the proportion of correct choices. 
As a recent paper by @pronk2021methods suggested, there are various less well-known split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design. To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position. First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling. Analyses were run using the function `by_split` from the `splithalfr` package [@pronk2021methods].
Second, we assessed the test-retest reliability. We calculated performance scores (depending on study version as described above) for each individual in each test session and correlated those using *Pearson* correlation coefficients. Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach. We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`). For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
The model computes a correlation between the participant specific estimates for each test day. This can be interpreted as the test-retest reliability. By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information. Most importantly, the model allows us to get an age-independent estimate for reliability. This rules out the possibility that a high correlation between test days arises from domain general cognitive maturation processes instead of study-specific inter-individual differences.

@@

# Exploring the external validity of our task
Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings.

```{r extvali_sample}
extvali <- testtrials %>% 
  filter(ageInYears < 6) %>%
  mutate(
        symmetricPosition = case_when(
                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1, 
                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3, 
                                  targetPosition == "2" | targetPosition == "9" ~ 4,
                                  targetPosition == "1" | targetPosition == "10" ~ 5, 
                       ), 
  ) %>% 
  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, symmetricPosition) %>% 
  group_by(subjID) %>% 
  # so that all models run with same nr of subjects
  drop_na()

@@

## Analysis
To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version). The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants. Therefore, our null model closely resembled the structure from our first analysis (section *Does the balloon finding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`). 
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome. For the target position, we categorized two adjacent bins as one imaginary box. To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box. Across the two study versions, we could consequently model the participant's correct response (0/1) using a Bernoulli distribution with a logit link function.
For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare. 
In addition, we calculated three index scores. First, we calculated a sibling variety score according to @peterson2000kindred. Second, we implemented the modified version of @cassidy2005theory (for more details, see Supplements). Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed). 
We compared the models using WAIC (widely applicable information criterion) scores and weights. As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit. WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

## Results
```{r extvali_winningmodel}
mExtvaliPE <- readRDS(file = "../saves/extvali-mExtvaliPE.rds") 
```

The model including our peer exposure index, as defined as the number of other children in the household and average hours spent in childcare, showed the best out-of-sample predictive accuracy. Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero. For example, for our winning model, we found an estimate of
`r fixef(mExtvaliPE)["pe", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["pe", "Q2.5"]`; `r fixef(mExtvaliPE)["pe", "Q97.5"]`]),
with the estimates of age being `r fixef(mExtvaliPE)["age", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["age", "Q2.5"]`; `r fixef(mExtvaliPE)["age", "Q97.5"]`]), data collection mode being `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q97.5"]`]), and study version `r fixef(mExtvaliPE)["studyversionbox", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["studyversionbox", "Q2.5"]`; `r fixef(mExtvaliPE)["studyversionbox", "Q97.5"]`]). Nevertheless, a general direction of effect can be seen: there seems to be small evidence that a social surrounding positively influenced children's gaze cue understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to follow the agent's gaze. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the more likely children found the target.

(ref:figlab4) **External validity of the balloon finding task**. 
Factors of children's social surroundings and their influence on the probability of responding correctly. Models are ordered according to their WAIC scores, with the uppermost winning the model comparison. The graph shows the estimated density curves of a model's predictor coefficient. Red tails display the 2.5% and 97.5% quantiles, respectively.

```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
knitr::include_graphics("../figures/extvali-posteriorsample.png")
```

## Discussion
Factors of children's social surrounding influenced their gaze cue understanding performance only slightly. Nevertheless, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables at all.

# Discussion
We were able to show that our balloon finding task measures inter-individual variation between children and adults, alike. Our results suggest that the measured variation is systematic during the course of the same and different test days. Impressively, the ability that our task measures related to factors in children's everyday life experience.

## Limitations
## Future development / extending the task

@@

#### WAIC scores and weights of the model comparison
As can be seen, ELPD difference scores are smaller than their respective standard errors. WAIC scores between models don't differ substantially. All effects except when a child entered childcare positively influence performance.

```{r extvali_results}
extvali_models <- readRDS(file = "../saves/extvali-results.rds")
knitr::kable(extvali_models)
```

### 2022-04-08 paper/manuscript.tex
review ext vali section

To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version). The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants. Therefore, our null model closely resembled the structure from our first analysis (section \emph{Does the balloon finding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome. For the target position, we summarized the two adjacent bins into one imaginary box. For the click responses, we created imaginary box boundaries around the target's landing position and assessed whether the participant's response fell into this imaginary box. Across the two study versions, we could consequently model the participant's correct response (0/1) using a Bernoulli distribution with a logit link function.
For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subjects entered childcare.
In addition, we calculated three index scores. First, we calculated a sibling variety score according to Peterson (2000). Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005) (for more details, see Supplements). Third, based on our own data exploration we calculated the amount of peer exposure as the number of siblings and the average hours spent in childcare (all z-transformed).
We compared the models using WAIC (widely applicable information criterion) scores and weights. As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit. WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

@@

{[}TODO{]} All effects except when a child entered childcare positively influence performance.
The effect sizes are all small and 95\% CIs mostly include zero. It is remarkable, however, that we were able to detect a relationship between a fundamental social-cognitive ability and very distant, real life demographics.

@@

\caption{\textbf{External validity of the balloon finding task}.
{[}TODO{]} WAIC scores and weights can be found in the Supplements section.}\label{fig:fig4}
\end{figure}

\hypertarget{discussion-2}{%
\section{Discussion}\label{discussion-2}}

@@

\begin{tabular}{l|r|r|r|r}
\hline
model & waic & waic\_weight & elpd\_diff & se\_diff\\
\hline
PE & 2391.092 & 0.4516270 & 0.0000000 & 0.0000000\\
\hline
siblingsVarietyScoreP & 2391.433 & 0.2009621 & -0.1703600 & 1.1084142\\
\hline
siblingsVarietyScoreW & 2391.612 & 0.0489847 & -0.2602340 & 1.1033051\\
\hline
hhSibs & 2391.654 & 0.0932701 & -0.2809574 & 0.9592453\\
\hline
null & 2391.963 & 0.0003588 & -0.4355391 & 1.3235267\\
\hline
ccAge & 2392.770 & 0.2047406 & -0.8390844 & 1.7165235\\
\hline
sibsChildAged & 2393.059 & 0.0000352 & -0.9836425 & 1.0349722\\
\hline
ccHours & 2393.156 & 0.0000134 & -1.0320103 & 1.0784916\\
\hline
hhTotal & 2393.647 & 0.0000082 & -1.2775838 & 0.9703247\\
\hline
\end{tabular}

>>>>

To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version). The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants. Therefore, our null model closely resembled the structure from our first analysis (section \emph{Does the balloon finding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome. For the target position, we categorized two adjacent bins as one imaginary box. To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box. Across the two study versions, we could consequently model the participant's correct response (0/1) using a Bernoulli distribution with a logit link function.
For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
In addition, we calculated three index scores. First, we calculated a sibling variety score according to Peterson (2000). Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005) (for more details, see Supplements). Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
We compared the models using WAIC (widely applicable information criterion) scores and weights. As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit. WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

@@

The model including our peer exposure index, as defined as the number of other children in the household and average hours spent in childcare, showed the best out-of-sample predictive accuracy. Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero. For example, for our winning model, we found an estimate of
0.18 (95\% CI {[}-0.01; 0.36{]}),
with the estimates of age being 0.59 (95\% CI {[}0.40; 0.79{]}), data collection mode being 0.93 (95\% CI {[}0.54; 1.34{]}), and study version 1.84 (95\% CI {[}0.14; 3.47{]}). Nevertheless, a general direction of effect can be seen: there seems to be small evidence that a social surrounding positively influenced children's gaze cue understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to follow the agent's gaze. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the more likely children found the target.

@@

\caption{\textbf{External validity of the balloon finding task}.
Factors of children's social surroundings and their influence on the probability of responding correctly. Models are ordered according to their WAIC scores, with the uppermost winning the model comparison. The graph shows the estimated density curves of a model's predictor coefficients. Red tails display the 2.5\% and 97.5\% quantiles, respectively.}\label{fig:fig4}
\end{figure}

\hypertarget{discussion-2}{%
\subsection{Discussion}\label{discussion-2}}

Factors of children's social surrounding influenced their gaze cue understanding performance only slightly. Nevertheless, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables at all.

\hypertarget{discussion-3}{%
\section{Discussion}\label{discussion-3}}

We were able to show that our balloon finding task measures inter-individual variation between children and adults, alike. Our results suggest that the measured variation is systematic during the course of the same and different test days. Impressively, the ability that our task measures related to factors in children's everyday life experience.

@@

\begin{tabular}{l|r|r|r|r}
\hline
model & waic & waic\_weight & elpd\_diff & se\_diff\\
\hline
PE & 2390.222 & 0.5405439 & 0.0000000 & 0.0000000\\
\hline
siblingsVarietyScoreP & 2390.429 & 0.3408146 & -0.1032133 & 1.0951621\\
\hline
ccHours & 2391.667 & 0.0001320 & -0.7222674 & 1.0449378\\
\hline
hhTotal & 2391.965 & 0.0001205 & -0.8716164 & 0.9255789\\
\hline
hhSibs & 2392.245 & 0.0000189 & -1.0114203 & 0.9762202\\
\hline
sibsChildAged & 2392.407 & 0.0000134 & -1.0924575 & 1.0418509\\
\hline
ccAge & 2392.445 & 0.1182920 & -1.1114913 & 1.6858011\\
\hline
null & 2392.618 & 0.0000583 & -1.1978484 & 1.2901087\\
\hline
siblingsVarietyScoreW & 2392.952 & 0.0000064 & -1.3648559 & 1.0877168\\
\hline
\end{tabular}
